---
title: "MA415 Final Project - A Glance at London Restaurants"
author: "Yue Wu"
date: "5/6/2018"
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
#install.packages("munsell")
library(munsell)
library(ggplot2)
library(dplyr)

data <- read_csv("tripadvisor_co_uk-travel_restaurant_reviews_sample.csv")

```


## Outline

- [Introduction](#3)
- [Dataset](#4)
- [Data Summary](#5)
- [Food score vs. overall score](#6)
- [Value score vs. overall score](#7)
- [Service score vs. overall score](#8)
- [Relationship among different scores](#9)
- [Linear Regression](#10)
- [Text Analysis on Review Text](#12)
- [Sentiment Analysis on Review Text](#13)
- [Text Analysis on Review Title](#17)
- [Sentiment Analysis on Review Title](#18)
- [Wordcloud](#19)
- [Map](#20)


## Introduction
This analysis focus on online reviews and scores for restaurants, especially the factors behind the scores. We will look at factors such as different sector scores and location. 


##What's the data set about?
- The dataset contains reviews and ratings of restaurants in the UK from year 2008 to 2017 from Tripadvisor. The goal is to take a closer look at factors behind the ratings, and how are restaurants in London overall.
- This dataset was created by PromptCloud's in-house web-crawling service. 
- Original dataset can be found [here](https://data.world/promptcloud/london-based-restaurants-reviews-on-tripadvisor-co-uk)

## Data Summary

The first thing to do is to better tidying the data Only desirable variables are kept, and rating related variables are transformed into numeric.

```{r clean, warning=FALSE, echo=FALSE}
data1 <- select(data,c("restaurant_id","name","review_date","title","review_text","author","location","rating","food","value","service","visited_on"))

## now get the count for each column
count<- apply(data1, 2, n_distinct)

#change rating variables to numeric
data2 <- data1 %>% 
          filter(str_detect(location, 'London')) %>%
          separate(rating,into= c("score","other"), sep= "of")  %>% 
          separate(food,into= c("food","fother"), sep= "of")  %>% 
          separate(value,into= c("value","vother"), sep= "of") %>% 
          separate(service,into= c("service","sother"), sep= "of") 
data2 <- data2 %>% select(-c(other,fother,vother,sother)) 

data2$score <- as.numeric(data2$score)
data2$food <- as.numeric(data2$food)
data2$value <- as.numeric(data2$value)
data2$service <- as.numeric(data2$service)

#group by restaurants
data3<- as.tibble(data2)
by_res <- data3 %>% group_by(name)


```
Here is the summary of the tidy data:
```{r kable, warning=FALSE, echo=FALSE,fig.height=6,fig.width=8}
library(knitr)
kable(summary(by_res[!names(by_res)=="restaurant_id"],na.rm=TRUE))
```


## food score vs. overall score

Now let's look at what we are interested in -- restaurant ratings and potential factors.<br>
From the t-test, we can see that the food score and overall score have significantly different means. 
```{r ttest1,eval=TRUE, echo= TRUE}
#t test on means of the scores
## overall score vs. food
t.test(by_res$score,by_res$food, na.action=na.omit)
```

## value score vs. overall score
The second t-test shows that value score also has a significantly different mean from the overall score.
```{r ttest2,eval=TRUE, echo= TRUE}
## overall score vs. value
t.test(by_res$score,by_res$value, na.action=na.omit)
```
## service score vs. overall score
The last t-test shows that service score also has a significantly different mean from the overall score.
```{r ttest3,eval=TRUE, echo= TRUE}
## overall score vs. service
t.test(by_res$score,by_res$service, na.action=na.omit)
```

## Relationship among Different Scores
- All three tests show that people rate food, value and service differently. The sector scores reflect specific aspects of a reviewer's experience, rather than a same reflection of their overall experience across the sectors.
- Let's take a better look at how different scores impact the overall score. Is the overall score simply the average of the other three scores?

## Linear Regression
```{r reg, eval=TRUE, echo=FALSE}
#linear regression
linearMod <- lm(score ~ food + value + service , data=by_res)
summary(linearMod)
#layout(matrix(c(1,2,3,4),2,2))
#plot(linearMod)
```

## Linear Regression
- It is safe to say that the overall score is not the average of the other three scores.
- More specifically, food score occupies more proportion in overall score components than the other two.
- Afterall, food is what a restaurant is mainly about.

## Text Analysis - Reviews
Enough with the scores, let's look at what people say in their reviews.<br>
Here are the top words in reviews:
```{r text, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
#text analysis
library(stringr)
library(tidytext)

## analysis on review_text
data4 <-separate(data3,visited_on,c("month","year"))
scores <- data4 %>%
  select(name,score,year) %>%
  group_by(name,year) %>%
  summarise(score = mean(score))

original_texts <- data4 %>% select(c("name","year","review_text")) %>%
                  group_by(name,year)
#data(stop_words)

tidy_reviews <- original_texts %>%
  unnest_tokens(word, review_text) %>% 
  ungroup() %>%
  anti_join(stop_words)

tidy_reviews %>%
  count(word, sort = TRUE) %>% head()

```
Again, food experience is very important to reviewers. We also see "service","staff" and "time" among the mostly used words, indicating the significance of service experience.

## Sentiment Analysis - Reviews
Reviewers express a lot of emotions in their reviews. How does sentiments in the reviews inpact the scores? Here is the sentiment-score analysis of reviews using the bing lexicon. Note that,
$$sentiment = n_{pos words} - n_{neg words}$$

```{r sent1, echo=FALSE, message=FALSE, warning=FALSE,fig.height=4}
###bing sentiments
bing_pos <- get_sentiments("bing") %>%
  filter(sentiment=="positive")
bing_neg <- get_sentiments("bing") %>%
  filter(sentiment=="negative")

###sentiment analysis
review_sentiments <- tidy_reviews %>%
  inner_join(get_sentiments("bing")) %>%
  count(name, year, sentiment, sort = TRUE) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  inner_join(scores)

### plots of sentiment on scores
review_plot <- ggplot(review_sentiments, aes(score, sentiment,color=year))
review_plot +
  geom_point(show.legend = FALSE) +
  coord_cartesian(ylim = c(-15, 180)) 
```

## Sentiment Analysis - Reviews
We see a positive relationship between sentiment and scores, except around score of 5. This could be due to a decrease in overall word counts for full-score reviews. Typically, those giving full scores can feel less needs to give detailed reviews. -- Don't we all rate our Uber drivers 5 stars when things go well?
```{r sent2, echo=FALSE, message=FALSE, warning=FALSE}
#### scatter with smooth line
review_plot +
  stat_smooth(se=F)
```

## Sentiment Analysis - Regression
Using linear regression, we can see that sentiment definitely has a positive relationship with score. The magnitude of the correlation varies lightly between different years. 
```{r sent3, echo=FALSE, message=FALSE, warning=FALSE}
### regression analysis
linearMod2 <- lm(sentiment ~ score , data=review_sentiments)
summary(linearMod2)
```

## Sentiment Analysis - Regression
```{r sent3_2, echo=FALSE, message=FALSE, warning=FALSE}
review_plot +
  geom_point(show.legend = FALSE) +
  geom_smooth(method='lm',formula=y~x,se=F)
```

## Text Analysis - Review Titles
Let's also look at the texts in the review titles. <br>
Again, "food" is the top word.
```{r sent4, echo=FALSE, message=FALSE, warning=FALSE}
## analysis on review title
original_titles <- data4 %>% select(c("name","year","title")) %>%
  group_by(name,year)
tidy_titles <- original_titles %>%
  unnest_tokens(word, title) %>% 
  ungroup()%>%
  anti_join(stop_words)

tidy_titles %>%
  count(word, sort = TRUE)
```

## Sentiment Analysis - Review Titles
Looking at the sentiments of review titles, we see a much smaller range of sentiment values, which can be a result of the shorter length of titles. <br>
However, there is still a positive correlation between title sentiment and scores.  
```{r sent5, echo=FALSE, message=FALSE, warning=FALSE}
###sentiment analysis
title_sentiments <- tidy_titles %>%
  inner_join(get_sentiments("bing")) %>%
  count(name, year, sentiment, sort = TRUE) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  inner_join(scores)

### plots of sentiment on scores
title_plot <- ggplot(title_sentiments, aes(score, sentiment,color=year))
title_plot +
  geom_point(show.legend = FALSE) +
  coord_cartesian(ylim = c(-10, 45)) 
```

## Wordclouds
Review Text Cloud               |               Review Title Cloud
--------------------------------|--------------------------------------
```{r wc1,echo=FALSE,warning=FALSE,message=FALSE,fig.height=5,fig.width=4.7}
### review wordcloud
library(wordcloud)
library(reshape2)
library(tidytext)
tidy_reviews %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),scale=c(3,0.2),
                   max.words = 200,main="Review Text Cloud")
```
|
```{r wc2,echo=FALSE,warning=FALSE,message=FALSE,fig.height=5,fig.width=4.5}
tidy_titles %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"), scale=c(3,0.2),
                   max.words = 200)
```

## Fantastic Restaurants and Where to Find Them
Check out where good restaurants are located in London. 
<br> Note that central London has a lot of high-score restaurants, as well as low-score ones. 
<br> There are areas with higher density of low-score than high-score places - Be aware!
```{r map, echo=FALSE, message=FALSE, warning=FALSE}
# map of the restaurants
library(ggmap)
london <- geocode("london, england")
map <- get_map(london, zoom=11)    ##modify the map location to adjust the view

# data frame with name and avg score
avg_score <- scores %>% group_by(name) %>%
  summarise(avg_score=mean(score, na.rm = TRUE))

# high variable: 1 if avg_score higher than 4
avg_score$high<- as.numeric(avg_score$avg_score>=4)
avg_score$high <- cut(avg_score$high, breaks = c(0,0.1,1), labels = c(0,1)) 

# geocodes for the restaurants
## pre-downloaded geocodes
load("data1.RData")
#avg_score$geo <- geocode(paste(avg_score$name,"london, england", sep=", "))
circle_scale_amt = 0.3

# map with circle size depending on avg score
ggmap(map) +
  geom_point(
    aes(x = geo$lon, y = geo$lat, colour = score),
    data = avg_score,
    alpha=0.4, size=(avg_score$score^2)*circle_scale_amt)+ 
  scale_size_continuous(range=range(avg_score$score)) +
  scale_color_distiller(type = "seq", palette = "Spectral")
```

> ggmap: Spatial Visualization with ggplot2.